BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web

### 2013-11-01 tex/3-architecture.tex
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
Improve score from 68.2% to 73.7% by taking top queries for all pages for the feed and not only the first one.

@@

>>>>

\begin{enumerate}
  \item Stateless
  \item Trade of efficiency for addaptability
  \item Stuctural maintenence is given because by recompute them each time
\end{enumerate}

@@

While some (Archiving Data Objects using Web Feeds -> Perenniality of Web archives.) take the

Google Blogspot Dynamic Views: \surl{http://buzz.blogger.com/2012/02/dynamic-views-update-3-gadgets.html}, \surl{https://support.google.com/blogger/answer/1229061?hl=en}
